Quantity discrimination, decision-making, and the role of early-life conditions in a lizard 

### 2025-03-17 ms.qmd
updates

---
title: "Quantity discrimination in the common garden skink and the role of early-life conditions"
docx: 
  reference-doc: "./bib/tmpl.docx"
bibliography: "./bib/refs.bib"
csl: "./bib/behavioral-ecology-and-sociobiology.csl"
execute:
  echo: false
  error: false
  cache: false
  warning: false
link-citations: true
crossref:  
  fig-title: Fig    # (default is "Figure")
  title-delim: —     # (default is ":")
  fig-prefix: Fig.   # (default is "Figure")
  tbl-prefix: Table  # (default is "Table")
editor_options: 
  chunk_output_type: console
---

@@

Pablo Recio^1^,$\ddagger$ , Dalton C. Leibold^1^, Ondi L. Crino ^1,2^, Christopher R. Friesen^3^, Amelia Y. Peardon ^1^, Daniel W.A. Noble^1^

^1^ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2601, Australia  
^2^ College of Science and Engineering, Flinders University, Bedford Park, SA 5042, Australia 
^3^ University of Wollongong, Wollongong, NSW 2500, Australia  
$\ddagger$ Corresponding author: pablo.reciosantiago@anu.edu.au

@@

_Table S4.- Number of individuals per treatment that chose the right (R) or left (L) side in each of the numerical tests. p-value indicates the result of the binomial test comparing the number of choices between sides. 
```{r, tbl-sides}
#| label: tbl-sides
#| tbl-cap: "Number of individuals per treatment that chose the right (R) or left (L) side in each of the numerical tests. p-value indicates the result of the binomial test comparing the number of choices between sides."
source(here("R", "func.R"))
#
# 1) MAKING THE DF FOR THE TABLE
data_sides <- data_num %>%
  group_by(trt, test_type) %>% # Group by treatment and test
  summarise(
    right_choices = sum(side_choice == "Right", na.rm = TRUE),
    left_choices = sum(side_choice == "Left", na.rm = TRUE),
  ) %>% # Count the number of correct choices
  rowwise() %>%  # Ensure that mutate works row by row
  mutate(
    total_choices = right_choices + left_choices,  # Calculate total choices
    p_value = format_dec(binom.test(right_choices, total_choices)$p.value, 2)  # Perform binom test
  ) %>% # Test for differences between sides
  ungroup() %>%  # Remove rowwise grouping
  mutate(choices_Right_Left_p = paste0("R = ", right_choices, " | L = ", left_choices, " , p = ", p_value), # Create a column with the choices
        trt = recode(trt, 
                 "B_23" = "CORT-Cold (n = 20)", 
                 "A_23" = "Control-Cold (n = 20)", 
                 "B_28" = "CORT-Hot (n = 20)", 
                 "A_28" = "Control-Hot (n = 20)")) %>% # To order the treatments
  dplyr::select(trt, test_type, choices_Right_Left_p) %>% # Remove unused columns
  pivot_wider(names_from = test_type, values_from = c(choices_Right_Left_p)) %>% # To split between tests
data.frame()
#
# 2) MAKING THE TABLE
#
# Split the table_data df by task
sides_table <- flextable(data_sides) %>%
  compose(j = 1, value = as_paragraph(""), part = "header") %>%
  compose(j = 2, value = as_paragraph("1 VS 4"), part = "header") %>%
  compose(j = 3, value = as_paragraph("1 VS 3"), part = "header") %>%
  compose(j = 4, value = as_paragraph("2 VS 4"), part = "header") %>%
  compose(j = 5, value = as_paragraph("2 VS 3"), part = "header") %>%
  compose(j = 6, value = as_paragraph("3 VS 4"), part = "header") %>%
  set_table_properties( width = 0.9, layout = "autofit") %>%
  align(align = "center", part = "all")
sides_table
```

>>>>

---
title: "Quantity discrimination, decision-making, and the role of early-life conditions in a lizard "
docx: 
  reference-doc: "./bib/tmpl.docx"
bibliography: "./bib/refs.bib"
csl: "./bib/behavioral-ecology-and-sociobiology.csl"
execute:
  echo: false
  error: false
  cache: false
  warning: false
link-citations: true
crossref:  
  fig-title: Fig    # (default is "Figure")
  title-delim: —     # (default is ":")
  fig-prefix: Fig.   # (default is "Figure")
  tbl-prefix: Table  # (default is "Table")
editor_options: 
  chunk_output_type: console
---

@@

Pablo Recio^1^,$\ddagger$ , Dalton C. Leibold^1^, Ondi L. Crino ^1,2^, Christopher R. Friesen ^3,4^, Amelia Y. Peardon ^1^, Daniel W.A. Noble^1^

^1^ Division of Ecology and Evolution, Research School of Biology, The Australian National University, Canberra, ACT 2601, Australia

^2^ College of Science and Engineering, Flinders University, Bedford Park, SA 5042, Australia

^3^ University of Wollongong, Wollongong, NSW 2500, Australia

^4^ Environmental Futures University of Wollongong, Wollongong, NSW, Australia

$\ddagger$ Corresponding author: pablo.reciosantiago@anu.edu.au

@@

_Table S4.- Number of individuals per treatment that chose the right (R) or left (L) side in each of the numerical tests. p-value indicates the result of the binomial test comparing the number of choices between sides._ 
```{r, tbl-sides}
#| label: tbl-sides
#| tbl-cap: "Number of individuals per treatment that chose the right (R) or left (L) side in each of the numerical tests. p-value indicates the result of the binomial test comparing the number of choices between sides."
source(here("R", "func.R"))
#
# 1) MAKING THE DF FOR THE TABLE
data_sides <- data_num %>%
  group_by(trt, test_type) %>% # Group by treatment and test
  summarise(
    right_choices = sum(side_choice == "Right", na.rm = TRUE),
    left_choices = sum(side_choice == "Left", na.rm = TRUE),
  ) %>% # Count the number of correct choices
  rowwise() %>%  # Ensure that mutate works row by row
  mutate(
    total_choices = right_choices + left_choices,  # Calculate total choices
    p_value = format_dec(binom.test(right_choices, total_choices)$p.value, 2)  # Perform binom test
  ) %>% # Test for differences between sides
  ungroup() %>%  # Remove rowwise grouping
  mutate(choices_Right_Left_p = paste0("R = ", right_choices, " | L = ", left_choices, " , p = ", p_value), # Create a column with the choices
        trt = recode(trt, 
                 "B_23" = "CORT-Cold (n = 20)", 
                 "A_23" = "Control-Cold (n = 20)", 
                 "B_28" = "CORT-Hot (n = 20)", 
                 "A_28" = "Control-Hot (n = 20)")) %>% # To order the treatments
  dplyr::select(trt, test_type, choices_Right_Left_p) %>% # Remove unused columns
  pivot_wider(names_from = test_type, values_from = c(choices_Right_Left_p)) %>% # To split between tests
data.frame()
#
# 2) MAKING THE TABLE
#
# Split the table_data df by task
sides_table <- flextable(data_sides) %>%
  compose(j = 1, value = as_paragraph(""), part = "header") %>%
  compose(j = 2, value = as_paragraph("1 VS 4"), part = "header") %>%
  compose(j = 3, value = as_paragraph("1 VS 3"), part = "header") %>%
  compose(j = 4, value = as_paragraph("2 VS 4"), part = "header") %>%
  compose(j = 5, value = as_paragraph("2 VS 3"), part = "header") %>%
  compose(j = 6, value = as_paragraph("3 VS 4"), part = "header") %>%
  set_table_properties( width = 0.9, layout = "autofit") %>%
  align(align = "center", part = "all")
sides_table
```
